Classifying Human Driving Behavior via Deep Neural Networks

### 2017-05-29 paper/paper-DrexelFormat.tex
updated paper - ch5

\subsection{Analysis of MAE and SAE}

>>>>

\subsection{Analysis Training LSTM in SAE and MAE}
The difference between {\em first model} and other models is that other models have AE. Therefore, AE layer from {\em second model} and {\em third model} caused worse performance. The first evidence of this can be implied from training process. Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show accuracy on each iterations during training. Figure \ref{fig:sae_loss} and Figure \ref{fig:mae_loss} show loss (error) on each iterations during training. Table \ref{tbl:sae_16_accuracy}, Table \ref{tbl:sae_32_accuracy}, Table \ref{tbl:sae_64_accuracy}, Table \ref{tbl:sae_128_accuracy}, and Table \ref{tbl:sae_256_accuracy} show detail of SAE train accuracy of 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons. Table \ref{tbl:mae_16_accuracy}, Table \ref{tbl:mae_32_accuracy}, Table \ref{tbl:mae_64_accuracy}, Table \ref{tbl:mae_128_accuracy}, and Table \ref{tbl:mae_256_accuracy} show detail of MAE train accuracy of 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons. Training LSTM in {\em second model} and {\em third model} were slow and most cases did not reach accurach 1 (100\%) unlikely that training LSTM in {\em first model} easily reached accuracy 1 (100\%). it implies data fed to LSTM has noise or problems. It means that AE in {\em second model} and {\em third model} did not work correctly.

\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{pictures/result_pictures/SAE_Accuracy.png}
    \caption{SAE Training Accuracy}
    \label{fig:sae_accuracy}
\end{figure}

\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{pictures/result_pictures/SAE_Loss.png}
    \caption{SAE Training Loss}
    \label{fig:sae_loss}
\end{figure}

\begin{table}[!t]
\centering
\caption{SAE, 16 Neuron Training Accuracy}
\label{tbl:sae_16_accuracy}
\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11} 
                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11} 
                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
\end{tabular}}
\end{table}

\begin{table}[!t]
\centering
\caption{SAE, 32 Neuron Training Accuracy}
\label{tbl:sae_32_accuracy}
\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11} 
                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11} 
                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
\end{tabular}}
\end{table}

\begin{table}[!t]
\centering
\caption{SAE, 64 Neuron Training Accuracy}
\label{tbl:sae_64_accuracy}
\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11} 
                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11} 
                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
\end{tabular}}
\end{table}

\begin{table}[!t]
\centering
\caption{SAE, 128 Neuron Training Accuracy}
\label{tbl:sae_128_accuracy}
\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11} 
                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11} 
                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
\end{tabular}}
\end{table}

\begin{table}[!t]
\centering
\caption{SAE, 256 Neuron Training Accuracy}
\label{tbl:sae_256_accuracy}
\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11} 
                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11} 
                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
\end{tabular}}
\end{table}

\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{pictures/result_pictures/MAE_Accuracy.png}
    \caption{MAE Training Accuracy}
    \label{fig:mae_accuracy}
\end{figure}

\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{pictures/result_pictures/MAE_Loss.png}
    \caption{MAE Training Loss}
    \label{fig:mae_loss}
\end{figure}

\begin{table}[!t]
\centering
\caption{MAE, 16 Neuron Training Accuracy}
\label{tbl:mae_16_accuracy}
\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11} 
                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11} 
                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
\end{tabular}}
\end{table}

\begin{table}[!t]
\centering
\caption{MAE, 32 Neuron Training Accuracy}
\label{tbl:mae_32_accuracy}
\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11} 
                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11} 
                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
\end{tabular}}
\end{table}

\begin{table}[!t]
\centering
\caption{MAE, 64 Neuron Training Accuracy}
\label{tbl:mae_64_accuracy}
\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11} 
                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11} 
                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11} 
                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11} 
                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11} 
                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11} 
